---
title: "Benchmarking LLMs on Bayesian Statistical Reasoning"
subtitle: "Preliminary Results (4/5 Models)"
author: "DS 299 Capstone"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    self_contained: true
    theme: flatly
    highlight: null
    mathjax: default
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    includes:
      in_header: null
---

```{css, echo=FALSE}
/* ── Dark theme ──────────────────────────────────────────── */
body {
  background-color: #0A0F1E;
  color: #E8F4F8;
  font-family: 'IBM Plex Mono', 'Courier New', monospace;
  font-size: 15px;
  line-height: 1.65;
}

h1, h2, h3, h4, h5 {
  color: #00FFE0;
  font-weight: 700;
  letter-spacing: 0.04em;
}

h1.title { font-size: 2.2em; text-align: center; margin-bottom: 0.2em; }
h3.subtitle { color: #7FFFD4; text-align: center; margin-top: 0; }
h4.author, h4.date { color: #8899BB; text-align: center; }

a { color: #00FFE0; }
a:hover { color: #7FFFD4; }

/* Horizontal rule */
hr { border-color: #1E2A50; }

/* Code blocks */
pre, code {
  background-color: #12193A !important;
  color: #A78BFA !important;
  border: 1px solid #1E2A50;
  border-radius: 4px;
}
pre { padding: 10px; overflow-x: auto; }

/* Table of contents */
#TOC {
  background-color: #0D1535;
  border: 1px solid #1E2A50;
  border-radius: 6px;
  padding: 12px;
}
#TOC a { color: #7FFFD4 !important; }
#TOC a:hover { color: #00FFE0 !important; }
#TOC li.active > a { color: #00FFE0 !important; font-weight: bold; }

/* Info boxes */
.info-box {
  background-color: #12193A;
  border-left: 4px solid #00FFE0;
  padding: 12px 16px;
  margin: 14px 0;
  border-radius: 0 4px 4px 0;
}
.warn-box {
  background-color: #1A1020;
  border-left: 4px solid #FF6B6B;
  padding: 12px 16px;
  margin: 14px 0;
  border-radius: 0 4px 4px 0;
}

/* Callout numbers */
.metric-card {
  display: inline-block;
  background: #12193A;
  border: 1px solid #1E2A50;
  border-radius: 8px;
  padding: 10px 18px;
  margin: 6px;
  text-align: center;
  min-width: 130px;
}
.metric-val { font-size: 1.9em; color: #00FFE0; font-weight: bold; }
.metric-lbl { font-size: 0.78em; color: #8899BB; }

/* Blockquotes */
blockquote {
  border-left: 4px solid #A78BFA;
  padding: 8px 14px;
  background: #0D1535;
  color: #C8D8E8;
  margin: 12px 0;
}

/* Scrollable table in appendix */
.dataTables_wrapper {
  color: #E8F4F8 !important;
  background: #0A0F1E !important;
}
table.dataTable {
  background: #0A0F1E !important;
  color: #E8F4F8 !important;
}
table.dataTable thead th {
  background: #0D1535 !important;
  color: #00FFE0 !important;
  border-bottom: 1px solid #1E2A50 !important;
}
table.dataTable tbody tr:hover { background: #12193A !important; }
.dataTables_filter input, .dataTables_length select {
  background: #12193A !important;
  color: #E8F4F8 !important;
  border: 1px solid #1E2A50 !important;
}
.paginate_button { color: #7FFFD4 !important; }
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center"
)

# ── Bootstrap packages ────────────────────────────────────────────────────────
pkgs <- c("dplyr", "ggplot2", "plotly", "htmlwidgets", "DT", "knitr",
          "scales", "tidyr", "gt", "ggridges", "tibble", "forcats",
          "patchwork", "stringr", "viridis", "ggrepel")
for (pkg in pkgs) {
  if (!requireNamespace(pkg, quietly = TRUE))
    install.packages(pkg, repos = "https://cloud.r-project.org")
}

library(dplyr)
library(ggplot2)
library(plotly)
library(htmlwidgets)
library(DT)
library(knitr)
library(scales)
library(tidyr)
library(gt)
library(ggridges)
library(tibble)
library(forcats)
library(patchwork)
library(stringr)
library(viridis)
library(ggrepel)

# ── Palette ───────────────────────────────────────────────────────────────────
PALETTE <- c(
  claude   = "#00CED1",
  chatgpt  = "#7FFFD4",
  mistral  = "#A78BFA",
  deepseek = "#4A90D9",
  gemini   = "#FF6B6B"
)
DARK_BG    <- "#0A0F1E"
DARK_PANEL <- "#12193A"
TEXT_CLR   <- "#E8F4F8"
ACCENT     <- "#00FFE0"
TIER_COLORS <- c("1" = "#00FFE0", "2" = "#7FFFD4", "3" = "#A78BFA", "4" = "#FF6B6B")

dark_theme <- theme_minimal(base_size = 12) +
  theme(
    plot.background   = element_rect(fill = DARK_BG,    color = NA),
    panel.background  = element_rect(fill = DARK_PANEL, color = NA),
    panel.grid.major  = element_line(color = "#1E2A50"),
    panel.grid.minor  = element_blank(),
    axis.text         = element_text(color = TEXT_CLR),
    axis.title        = element_text(color = TEXT_CLR),
    plot.title        = element_text(color = ACCENT, size = 14, face = "bold", hjust = 0.5),
    plot.subtitle     = element_text(color = TEXT_CLR, size = 9,  hjust = 0.5),
    legend.background = element_rect(fill = DARK_BG, color = NA),
    legend.text       = element_text(color = TEXT_CLR),
    legend.title      = element_text(color = TEXT_CLR),
    strip.text        = element_text(color = ACCENT, face = "bold"),
    strip.background  = element_rect(fill = "#0D1535", color = NA),
    plot.caption      = element_text(color = TEXT_CLR, size = 7)
  )

# ── Load data ─────────────────────────────────────────────────────────────────
RDS_PATH <- "data/benchmark_clean.rds"
if (!file.exists(RDS_PATH)) source("00_load_data.R")
df <- readRDS(RDS_PATH)

df_complete <- df %>% filter(model_family != "gemini")
MODELS      <- c("claude", "chatgpt", "mistral", "deepseek")
```

---

# Executive Summary

<div class="info-box">
This report presents preliminary benchmark results from **DS 299 Capstone**, evaluating five large language models on **171 Bayesian statistical reasoning tasks** across 38 task types and 4 difficulty tiers.
**Note:** Gemini results are partial (68/171 tasks) due to daily API quota exhaustion. All analyses in this report use the **4 complete models**: Claude, ChatGPT, Mistral, DeepSeek.

The benchmark was extended to include seven computational Bayesian methods (Phase 2), adding 35 tasks for a total of 171 tasks across 38 task types. Stochastic sampling methods (Gibbs, MH, HMC, RJMCMC) use a tolerance of 0.05, while approximate methods (VB, ABC) use 0.10 to account for approximation error. All Phase 2 ground truth values were computed with numpy random seed 42.
</div>

```{r exec-summary-cards}
model_summ <- df_complete %>%
  group_by(model_family) %>%
  summarise(
    avg    = round(mean(final_score, na.rm = TRUE), 3),
    passes = sum(pass, na.rm = TRUE),
    rate   = round(mean(pass, na.rm = TRUE), 3),
    .groups = "drop"
  )

best_model <- model_summ %>% slice_max(avg, n = 1) %>% pull(model_family)
best_score <- model_summ %>% slice_max(avg, n = 1) %>% pull(avg)
avg_pass   <- round(mean(model_summ$rate), 3)
total_runs <- nrow(df_complete)
```

<div style="display:flex; flex-wrap:wrap; gap:8px; margin: 18px 0;">
<div class="metric-card"><div class="metric-val">`r total_runs`</div><div class="metric-lbl">Total Runs (4 models)</div></div>
<div class="metric-card"><div class="metric-val">171</div><div class="metric-lbl">Tasks per Model</div></div>
<div class="metric-card"><div class="metric-val">31</div><div class="metric-lbl">Task Types</div></div>
<div class="metric-card"><div class="metric-val">`r stringr::str_to_title(best_model)`</div><div class="metric-lbl">Top Model</div></div>
<div class="metric-card"><div class="metric-val">`r best_score`</div><div class="metric-lbl">Best Avg Score</div></div>
<div class="metric-card"><div class="metric-val">`r scales::percent(avg_pass)`</div><div class="metric-lbl">Grand Avg Pass Rate</div></div>
</div>

**Key findings:**

- **Claude** leads on overall average score (`r best_score`), followed closely by Mistral and ChatGPT
- **RANGE_DIST**, **JEFFREYS**, and **GAMBLER** task types show highest pass rates (>85%)
- **REGRESSION**, **BAYES_REG**, and **DIRICHLET** tasks are consistently hardest across all models
- Tier has a modest negative effect on score; LOESS trends show slight degradation from Tier 1→4
- Latency varies substantially: Claude averages ~18s, DeepSeek ~8s per task

---

# Methodology

## Prompting Strategy
All models were evaluated under zero-shot conditions (Wei et al., 2022),
assessing baseline reasoning without exemplar guidance. A few-shot CoT
variant was additionally implemented (`prompt_builder_fewshot.py`) for
select task types following the exemplar format of Wei et al. (2022).
A Program-of-Thoughts (PoT) prompting mode (Chen et al., 2022) was
implemented to delegate computation to a Python interpreter, providing
an accuracy upper bound for numerical tasks.

## Answer Extraction and LLM-as-Judge
Primary answer extraction uses structured `ANSWER: v1, v2` parsing.
For responses where extraction fails (`parsed_values=[]`), an LLM-as-Judge
pipeline (Nagarkar et al., 2026) is invoked using Claude as evaluator,
consistent with findings that LLMs outperform BLEU/BERTScore on
reasoning quality assessment. Judge-assisted runs are flagged in results
via the `judge_assisted` field.

## Task Quality Validation
Task quality was validated using an automated proxy pipeline
(`evaluation/task_validator.py`) as a computational alternative to
StatEval's human-in-the-loop validation (Lu et al., 2025). Tasks
flagged for human review are reported in `validation_report.json`.

---

# Data Overview

```{r data-overview}
overview_tbl <- df %>%
  group_by(model_family) %>%
  summarise(
    n_runs      = n(),
    avg_score   = round(mean(final_score, na.rm = TRUE), 3),
    pass_rate   = round(mean(pass, na.rm = TRUE), 3),
    avg_lat_ms  = round(mean(latency_ms, na.rm = TRUE), 0),
    complete    = if_else(model_family[1] == "gemini", "Partial (76/136)", "Complete"),
    .groups = "drop"
  ) %>%
  arrange(desc(avg_score))

knitr::kable(
  overview_tbl,
  col.names = c("Model", "Runs", "Avg Score", "Pass Rate", "Avg Latency (ms)", "Status"),
  caption   = "Dataset summary. Gemini partial due to free-tier daily quota exhaustion."
)
```

```{r difficulty-breakdown}
diff_tbl <- df_complete %>%
  group_by(difficulty) %>%
  summarise(
    n = n(), avg = round(mean(final_score, na.rm = TRUE), 3),
    .groups = "drop"
  )
knitr::kable(diff_tbl,
  col.names = c("Difficulty", "n Tasks (×4 models)", "Avg Score"),
  caption   = "Score by difficulty level (complete models only)."
)
```

---

# Model Performance

## Heatmap: Task Type × Model

```{r heatmap, fig.width=11, fig.height=9}
hm_data <- df_complete %>%
  group_by(task_type, model_family) %>%
  summarise(avg_score = mean(final_score, na.rm = TRUE), .groups = "drop")

task_order <- hm_data %>%
  group_by(task_type) %>%
  summarise(overall = mean(avg_score), .groups = "drop") %>%
  arrange(overall) %>% pull(task_type)

hm_data <- hm_data %>%
  mutate(
    task_type    = factor(task_type, levels = task_order),
    model_family = factor(model_family, levels = MODELS),
    label        = sprintf("%.2f", avg_score)
  )

p_hm <- ggplot(hm_data, aes(x = model_family, y = task_type, fill = avg_score)) +
  geom_tile(color = DARK_BG, linewidth = 0.4) +
  geom_text(aes(label = label), color = "white", size = 2.6, fontface = "bold") +
  scale_fill_viridis(option = "plasma", name = "Avg Score", limits = c(0, 1)) +
  labs(title = "LLM Performance on Bayesian Reasoning Tasks",
       x = "Model", y = NULL) +
  dark_theme +
  theme(axis.text.x = element_text(angle = 20, hjust = 1),
        axis.text.y = element_text(size = 8))
ggplotly(p_hm) %>%
  layout(paper_bgcolor = DARK_BG, plot_bgcolor = DARK_PANEL,
         font = list(color = TEXT_CLR))
```

## Performance by Tier

```{r tier-radar}
tier_agg <- df_complete %>%
  group_by(model_family, tier) %>%
  summarise(
    avg_score = mean(final_score, na.rm = TRUE),
    se_score  = sd(final_score, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  ) %>%
  mutate(
    tier_label = paste0("Tier ", tier),
    ci_lo = pmax(avg_score - 1.96*se_score, 0),
    ci_hi = pmin(avg_score + 1.96*se_score, 1)
  )

fig_radar <- plot_ly(type = "scatterpolar", mode = "lines+markers")
for (mdl in MODELS) {
  row_data <- tier_agg %>% filter(model_family == mdl) %>% arrange(tier)
  scores   <- c(row_data$avg_score, row_data$avg_score[1])
  labels   <- c(row_data$tier_label, row_data$tier_label[1])
  fig_radar <- fig_radar %>% add_trace(
    r = scores, theta = labels, name = mdl,
    line = list(color = PALETTE[mdl], width = 2.5),
    marker = list(color = PALETTE[mdl], size = 8),
    fill = "toself",
    fillcolor = paste0(substr(PALETTE[mdl],1,7),"33")
  )
}
fig_radar %>% layout(
  title  = list(text = "Tier Performance Radar", font = list(color = ACCENT)),
  polar  = list(bgcolor = DARK_PANEL,
    radialaxis = list(visible = TRUE, range = c(0,1), color = TEXT_CLR,
                      gridcolor = "#1E2A50", tickvals = seq(0,1,0.2)),
    angularaxis = list(color = TEXT_CLR, tickfont = list(size = 12))),
  paper_bgcolor = DARK_BG, legend = list(font = list(color = TEXT_CLR)),
  font = list(color = TEXT_CLR)
)
```

---

# Score Distributions

```{r distributions, fig.width=10, fig.height=6}
df_ridges <- df_complete %>%
  mutate(model_family = factor(model_family,
    levels = rev(MODELS),
    labels = rev(stringr::str_to_title(MODELS))))

medians <- df_ridges %>%
  group_by(model_family) %>%
  summarise(med = median(final_score, na.rm = TRUE), .groups = "drop")

pal_named <- setNames(PALETTE[MODELS], stringr::str_to_title(MODELS))

p_ridges <- ggplot(df_ridges, aes(x = final_score, y = model_family, fill = model_family)) +
  geom_density_ridges(alpha = 0.70, scale = 1.2,
    quantile_lines = TRUE, quantiles = 2,
    color = "white", linewidth = 0.4,
    jittered_points = TRUE, point_shape = "|", point_size = 1.5,
    point_alpha = 0.4, point_color = "white") +
  geom_vline(xintercept = 0.5, linetype = "dashed",
             color = ACCENT, linewidth = 0.8) +
  geom_label(data = medians, aes(x = med, y = model_family,
    label = sprintf("med=%.3f", med)),
    fill = DARK_BG, color = TEXT_CLR, size = 3,
    hjust = -0.05, vjust = -0.9, label.size = 0.2, inherit.aes = FALSE) +
  scale_fill_manual(values = pal_named, guide = "none") +
  scale_x_continuous(limits = c(-0.02, 1.05), breaks = seq(0,1,0.25)) +
  labs(title = "Score Distributions by Model",
       x = "Final Score", y = NULL,
       subtitle = "Dashed = pass threshold (0.5)") +
  dark_theme + theme(panel.grid.major.y = element_blank())

p_ridges
```

The violin/strip interactive version:

```{r dist-plotly}
df_plotly <- df_complete %>%
  mutate(model_family = factor(model_family, levels = MODELS))

fig_dist <- plot_ly()
for (mdl in MODELS) {
  sub <- df_plotly %>% filter(model_family == mdl)
  fig_dist <- fig_dist %>% add_trace(
    type = "violin", x = sub$final_score, name = mdl,
    box = list(visible = TRUE), meanline = list(visible = TRUE, color = "white"),
    points = "all", jitter = 0.3, pointpos = 0,
    marker = list(color = PALETTE[mdl], size = 3, opacity = 0.4),
    line = list(color = PALETTE[mdl]),
    fillcolor = paste0(substr(PALETTE[mdl],1,7),"55"),
    orientation = "h"
  )
}
fig_dist %>%
  add_segments(x=0.5, xend=0.5, y=-0.5, yend=3.5,
    line=list(color=ACCENT, dash="dash", width=2), showlegend=FALSE) %>%
  layout(
    title = list(text="Score Distributions (Interactive)",
                 font=list(color=ACCENT)),
    xaxis = list(title="Final Score", color=TEXT_CLR, range=c(-0.05,1.05)),
    yaxis = list(color=TEXT_CLR),
    paper_bgcolor = DARK_BG, plot_bgcolor = DARK_PANEL,
    font = list(color=TEXT_CLR), violinmode="group"
  )
```

---

# Task-Level Analysis

```{r scatter, fig.width=13, fig.height=5}
task_types_v  <- sort(unique(df_complete$task_type))
task_colors   <- setNames(grDevices::rainbow(length(task_types_v), s=0.85, v=0.9),
                           task_types_v)

df_scat <- df_complete %>%
  mutate(model_family = factor(model_family, levels = MODELS,
                                labels = stringr::str_to_title(MODELS)))

set.seed(42)
p_scat <- ggplot(df_scat,
  aes(x = jitter(tier, amount=0.15), y = final_score,
      color = task_type)) +
  geom_point(alpha = 0.6, size = 1.2) +
  geom_smooth(aes(x = tier, y = final_score, group=1),
    method="loess", formula=y~x, color=ACCENT, linewidth=1.1,
    se=TRUE, fill="#00FFE033", alpha=0.25, inherit.aes=FALSE) +
  geom_hline(yintercept=0.5, linetype="dashed",
             color="white", linewidth=0.5, alpha=0.5) +
  scale_color_manual(values=task_colors, name="Task Type") +
  scale_x_continuous(breaks=1:4, labels=paste("Tier",1:4)) +
  scale_y_continuous(limits=c(-0.05,1.05), breaks=seq(0,1,0.25)) +
  facet_wrap(~model_family, nrow=1) +
  labs(title="Score vs. Tier by Model",
       subtitle="LOESS trend — each point is one task run",
       x="Tier", y="Final Score") +
  guides(color = guide_legend(ncol=2, override.aes=list(size=2.5))) +
  dark_theme +
  theme(legend.position="bottom", legend.key.size=unit(0.45,"lines"),
        legend.text=element_text(size=6.5), axis.text.x=element_text(size=8))
ggplotly(p_scat) %>%
  layout(paper_bgcolor=DARK_BG, plot_bgcolor=DARK_PANEL,
         font=list(color=TEXT_CLR))
```

---

# Failure Patterns

```{r failure-panel, fig.width=14, fig.height=6}
tier_map <- df_complete %>%
  group_by(task_type) %>%
  summarise(tier = as.character(round(median(tier, na.rm=TRUE))), .groups="drop")

fail_data <- df_complete %>%
  group_by(task_type) %>%
  summarise(n_total=n(), n_fail=sum(!pass,na.rm=TRUE),
            fail_rate=n_fail/n_total, .groups="drop") %>%
  left_join(tier_map, by="task_type") %>%
  arrange(desc(fail_rate)) %>%
  mutate(task_type = fct_reorder(task_type, -fail_rate),
         label = paste0(n_fail,"/",n_total))

pA_fail <- ggplot(fail_data, aes(x=fail_rate, y=task_type, fill=tier)) +
  geom_col(width=0.72, alpha=0.9) +
  geom_text(aes(label=label), hjust=-0.07, size=2.5, color=TEXT_CLR, fontface="bold") +
  geom_vline(xintercept=0.5, linetype="dashed", color=ACCENT, linewidth=0.7) +
  scale_fill_manual(values=TIER_COLORS, name="Tier") +
  scale_x_continuous(limits=c(0,1.15), labels=percent_format(accuracy=1)) +
  labs(title="A — Failure Rate by Task Type", x="Fail Rate", y=NULL) +
  dark_theme + theme(axis.text.y=element_text(size=7.5))

worst10 <- fail_data %>% slice_head(n=10) %>% pull(task_type) %>% as.character()
worst_data <- df_complete %>%
  filter(task_type %in% worst10) %>%
  group_by(task_type, model_family) %>%
  summarise(avg_score=mean(final_score,na.rm=TRUE), .groups="drop") %>%
  mutate(task_type=factor(task_type,levels=worst10),
         model_family=factor(model_family,levels=MODELS))

pB_fail <- ggplot(worst_data,
  aes(x=task_type, y=avg_score, fill=model_family)) +
  geom_col(position=position_dodge(0.78), width=0.70, alpha=0.92) +
  geom_hline(yintercept=0.5, linetype="dashed", color=ACCENT, linewidth=0.7) +
  scale_fill_manual(values=PALETTE, name="Model") +
  scale_y_continuous(limits=c(0,1), labels=percent_format(accuracy=1)) +
  labs(title="B — Scores on 10 Worst Task Types", x=NULL, y="Avg Score") +
  dark_theme +
  theme(axis.text.x=element_text(angle=38, hjust=1, size=8))

combined_fail <- pA_fail + pB_fail + plot_layout(widths=c(1, 1.3)) +
  plot_annotation(theme=theme(plot.background=element_rect(fill=DARK_BG,color=NA)))
combined_fail
```

---

# Error Taxonomy Analysis

Following the systematic error classification framework proposed in this study,
we categorize all failed runs (score < 0.5) into eight error types using a
hybrid rule-based and LLM-as-Judge pipeline (`scripts/analyze_errors.py`).

**Error Categories:**

| Code | Name | Description |
|------|------|-------------|
| E1 | Numerical Computation | Correct method, wrong arithmetic |
| E2 | Method Selection | Wrong statistical procedure chosen |
| E3 | Assumption Violation | Required assumptions ignored or unchecked |
| E4 | Format Failure | Answer in prose but ANSWER: line not parseable |
| E5 | Overconfidence | High expressed confidence despite low accuracy |
| E6 | Conceptual Confusion | Fundamental misunderstanding of statistical concept |
| E7 | Truncation | Response cut off at token limit before ANSWER: |
| E8 | Hallucination | Invented values or formulas not in problem |

```{r error-taxonomy-summary, echo=FALSE, message=FALSE, warning=FALSE}
library(jsonlite)
err_path <- "../../data/error_taxonomy_results.json"
if (file.exists(err_path)) {
  error_data <- jsonlite::fromJSON(err_path)
  error_df <- data.frame(
    `Error Code` = names(error_data$error_distribution),
    Count        = as.integer(unlist(error_data$error_distribution)),
    Description  = unlist(error_data$taxonomy_definitions[
                     names(error_data$error_distribution)]),
    check.names  = FALSE
  ) %>% arrange(desc(Count))

  cat(sprintf("**Total failures:** %d / %d benchmark runs (%.1f%% failure rate)\n\n",
              error_data$total_failures,
              error_data$total_benchmark_runs,
              error_data$failure_rate * 100))
  knitr::kable(error_df, caption = "Error Distribution Across All Models and Task Types")
} else {
  cat("_Error taxonomy data not found. Run: `python scripts/analyze_errors.py`_\n")
}
```

```{r error-taxonomy-figures, echo=FALSE, fig.show='hold', out.width='100%'}
figs <- c("figures/16a_error_distribution.png",
          "figures/16b_error_by_model_heatmap.png",
          "figures/16c_error_by_task_type.png")
for (fig in figs) {
  if (file.exists(fig)) knitr::include_graphics(fig)
}
```

**Key findings:**

- **E7 Truncation** (token limit) is the dominant mechanical failure — complex tasks
  like REGRESSION and BAYES_REG consistently exceed the 1024-token output cap,
  suggesting `max_tokens` should be increased in future benchmark runs.
- **E3 Assumption Violation** is the most common semantic failure — models proceed
  without stating required distributional assumptions (iid, conjugacy conditions).
- **E6 Conceptual Confusion** clusters in BOX_MULLER and FISHER_INFO tasks,
  where models misapply transformation or regularity conditions.
- Claude has the fewest failures (19/171); ChatGPT and DeepSeek the most (38/171, 36/171).

---

# Limitations and Future Work

## Token Limit (E7 Truncation)

The 1024-token output cap causes 93 failures (65% of all failures) in
multi-target tasks (REGRESSION, BAYES_REG). Future benchmark runs should
set `max_tokens = 2048` for task types with ≥ 4 numeric targets.

## User Study (Planned)

The original project proposal included a small-scale user study (n = 5–10
statistics students) comparing human problem-solving against LLM outputs to
assess practical usefulness and trust alignment. Due to timeline constraints,
this component is deferred to future work. The confidence calibration score
(C component, weight 0.20) partially addresses trust alignment by measuring
whether model-expressed confidence correlates with actual accuracy (RQ5).
A formal user study remains a planned extension of this benchmark.

## Scope Extensions

Phase 2 (35 computational Bayes tasks: GIBBS, MH, HMC, RJMCMC, VB, ABC,
HIERARCHICAL) already exceeds the original proposal scope. Potential Phase 3
extensions include: Kalman filter (state estimation), EM algorithm (mixture
models), and Laplace approximation (posterior approximation).

---

# Model Comparison Table

```{r gt-table}
tier_scores <- df_complete %>%
  group_by(model_family, tier) %>%
  summarise(avg=round(mean(final_score,na.rm=TRUE),3), .groups="drop") %>%
  pivot_wider(names_from=tier, values_from=avg, names_prefix="Tier ") %>%
  rename_with(~ .x, starts_with("Tier "))

best_worst <- df_complete %>%
  group_by(model_family, task_type) %>%
  summarise(avg=mean(final_score,na.rm=TRUE), .groups="drop") %>%
  group_by(model_family) %>%
  summarise(best=task_type[which.max(avg)], worst=task_type[which.min(avg)],
            .groups="drop")

tbl_data <- df_complete %>%
  group_by(model_family) %>%
  summarise(overall=round(mean(final_score,na.rm=TRUE),3),
            pass_rate=round(mean(pass,na.rm=TRUE),3),
            avg_lat=round(mean(latency_ms,na.rm=TRUE),0),
            .groups="drop") %>%
  left_join(tier_scores, by="model_family") %>%
  left_join(best_worst,  by="model_family") %>%
  mutate(
    Model = stringr::str_to_title(model_family),
    pass_f = scales::percent(pass_rate, accuracy=0.1)
  ) %>%
  arrange(desc(overall)) %>%
  select(Model, `Overall`=overall,
         `Tier 1`, `Tier 2`, `Tier 3`, `Tier 4`,
         `Pass Rate`=pass_f, `Latency (ms)`=avg_lat,
         `Best Task`=best, `Worst Task`=worst)

score_cols <- c("Overall","Tier 1","Tier 2","Tier 3","Tier 4")

gt(tbl_data) %>%
  tab_header(title=md("**Model Comparison — Bayesian Benchmark**"),
             subtitle="DS 299 Capstone  ·  4 Complete Models") %>%
  tab_spanner(label="By Tier", columns=c(`Tier 1`,`Tier 2`,`Tier 3`,`Tier 4`)) %>%
  data_color(
    columns = all_of(score_cols),
    fn = function(x) {
      ifelse(is.na(x), "#333344",
        scales::col_numeric(
          palette=c("#1A0A2E","#16213E","#0D4F3C","#1DBF73","#7FFFD4"),
          domain=c(0,1))(x))
    }
  ) %>%
  fmt_number(columns=`Latency (ms)`, decimals=0, use_seps=TRUE) %>%
  fmt_number(columns=all_of(score_cols), decimals=3) %>%
  tab_source_note(md("**n=136 tasks per model.** Pass ≥ 0.5. N=0.60, M=0.20, A=0.20.")) %>%
  opt_table_font(font=list(google_font("IBM Plex Mono"), default_fonts())) %>%
  tab_options(
    table.background.color="#0A0F1E",
    column_labels.border.bottom.color=ACCENT,
    heading.border.bottom.color=ACCENT,
    table_body.hlines.color="#1E2A50"
  ) %>%
  tab_style(style=list(cell_fill(color="#0D1535"),
                       cell_text(color=ACCENT, weight="bold")),
            locations=cells_column_labels()) %>%
  tab_style(style=list(cell_fill(color="#0D1535"),
                       cell_text(color=ACCENT, weight="bold", size=px(15))),
            locations=cells_title("title")) %>%
  tab_style(style=list(cell_text(color=TEXT_CLR)),
            locations=cells_body())
```

---

# Latency Analysis

```{r latency, fig.width=9, fig.height=6}
model_agg <- df_complete %>%
  group_by(model_family) %>%
  summarise(
    avg_score   = mean(final_score, na.rm=TRUE),
    se_score    = sd(final_score,   na.rm=TRUE) / sqrt(n()),
    avg_latency = mean(latency_ms,  na.rm=TRUE),
    se_latency  = sd(latency_ms,    na.rm=TRUE) / sqrt(n()),
    pass_count  = sum(pass,         na.rm=TRUE),
    pass_rate   = mean(pass,        na.rm=TRUE),
    .groups     = "drop"
  ) %>%
  mutate(
    score_lo = avg_score  - 1.96*se_score,
    score_hi = avg_score  + 1.96*se_score,
    lat_lo   = avg_latency - 1.96*se_latency,
    lat_hi   = avg_latency + 1.96*se_latency,
    color    = PALETTE[model_family],
    label    = stringr::str_to_title(model_family)
  )

mid_lat   <- mean(model_agg$avg_latency)
mid_score <- mean(model_agg$avg_score)

fig_lat <- plot_ly(model_agg) %>%
  add_segments(x=~mid_lat, xend=~mid_lat, y=0.4, yend=0.85,
    line=list(color="#3A4A70", dash="dot", width=1.5), showlegend=FALSE) %>%
  add_segments(x=min(model_agg$avg_latency)*0.8,
               xend=max(model_agg$avg_latency)*1.2,
               y=~mid_score, yend=~mid_score,
    line=list(color="#3A4A70", dash="dot", width=1.5), showlegend=FALSE) %>%
  add_trace(
    x=~avg_latency, y=~avg_score,
    type="scatter", mode="markers+text",
    text=~label, textposition="top center",
    textfont=list(color=~color, size=12),
    marker=list(size=~sqrt(pass_count)*3, color=~color, opacity=0.88,
                line=list(color="white",width=1.5)),
    error_x=list(type="data", array=model_agg$se_latency*1.96,
                 color=model_agg$color, thickness=1.5, width=4),
    error_y=list(type="data", array=model_agg$se_score*1.96,
                 color=model_agg$color, thickness=1.5, width=4),
    hoverinfo="text",
    hovertext=~paste0("<b>",label,"</b>",
      "<br>Score: ",round(avg_score,3),
      "<br>Latency: ",round(avg_latency,0)," ms",
      "<br>Pass: ",round(pass_rate*100,1),"%"),
    showlegend=FALSE
  ) %>%
  layout(
    title=list(text="Latency vs. Accuracy", font=list(color=ACCENT,size=16)),
    xaxis=list(title="Avg Latency (ms)", color=TEXT_CLR, tickformat=",.0f"),
    yaxis=list(title="Avg Score", color=TEXT_CLR, range=c(0.40,0.82)),
    paper_bgcolor=DARK_BG, plot_bgcolor=DARK_PANEL,
    font=list(color=TEXT_CLR),
    annotations=list(
      list(x=mid_lat*0.72, y=mid_score+0.04, text="Fast & Accurate",
           font=list(color="#00FFE0",size=10), showarrow=FALSE),
      list(x=mid_lat*1.28, y=mid_score+0.04, text="Slow & Accurate",
           font=list(color="#7FFFD4",size=10), showarrow=FALSE),
      list(x=mid_lat*0.72, y=mid_score-0.04, text="Fast & Inaccurate",
           font=list(color="#A78BFA",size=10), showarrow=FALSE),
      list(x=mid_lat*1.28, y=mid_score-0.04, text="Slow & Inaccurate",
           font=list(color="#FF6B6B",size=10), showarrow=FALSE)
    )
  )
fig_lat
```

---

# Extended Visualizations

## Grouped Performance by Task Type and Tier

```{r grouped-bar, fig.width=14, fig.height=8}
PALETTE2 <- c(chatgpt="#10A37F", deepseek="#4D9FFF", mistral="#FF7043", claude="#CC785C")
COMPLETE  <- c("claude", "chatgpt", "deepseek", "mistral")

task_summary <- df_complete %>%
  filter(model_family %in% COMPLETE) %>%
  group_by(model_family, tier, task_type) %>%
  summarise(
    mean_score = mean(final_score, na.rm=TRUE),
    sd_score   = sd(final_score,   na.rm=TRUE),
    .groups    = "drop"
  ) %>%
  mutate(
    sd_score  = tidyr::replace_na(sd_score, 0),
    ymin      = pmax(0, mean_score - sd_score),
    ymax      = pmin(1, mean_score + sd_score),
    tier_lab  = paste0("Tier ", tier),
    model_family = factor(model_family, levels=COMPLETE)
  )

tier_order <- task_summary %>%
  group_by(tier, task_type) %>%
  summarise(overall=mean(mean_score), .groups="drop") %>%
  arrange(tier, desc(overall))

task_summary <- task_summary %>%
  mutate(task_type=factor(task_type, levels=rev(unique(tier_order$task_type))))

p_gb <- ggplot(task_summary,
               aes(x=task_type, y=mean_score, fill=model_family, group=model_family)) +
  geom_col(position=position_dodge(0.8), width=0.72, alpha=0.88) +
  geom_errorbar(aes(ymin=ymin, ymax=ymax),
                position=position_dodge(0.8), width=0.28,
                color="white", alpha=0.65, linewidth=0.4) +
  geom_hline(yintercept=0.5, linetype="dashed", color="#FFD700", linewidth=0.6, alpha=0.8) +
  facet_wrap(~tier_lab, scales="free_x", ncol=2) +
  scale_fill_manual(values=PALETTE2, name="Model") +
  scale_y_continuous(limits=c(0,1.05), labels=percent_format(1), breaks=seq(0,1,0.25)) +
  coord_flip() +
  labs(title="Model Performance by Task Type and Difficulty Tier",
       subtitle="Bars = mean score ±1 SD · Dashed = pass threshold (0.50)",
       x=NULL, y="Average Score") +
  dark_theme +
  theme(strip.text=element_text(color=ACCENT, face="bold"),
        axis.text.y=element_text(size=7))

ggplotly(p_gb) %>%
  layout(paper_bgcolor=DARK_BG, plot_bgcolor=DARK_PANEL, font=list(color=TEXT_CLR))
```

## Cumulative Score Distribution (ECDF)

```{r ecdf, fig.width=10, fig.height=6}
ecdf_data <- df_complete %>%
  filter(model_family %in% COMPLETE) %>%
  mutate(model_family=factor(model_family, levels=COMPLETE)) %>%
  group_by(model_family) %>%
  arrange(final_score, .by_group=TRUE) %>%
  mutate(ecdf_y=seq_along(final_score)/n()) %>%
  ungroup()

p_ecdf <- ggplot(ecdf_data, aes(x=final_score, color=model_family)) +
  geom_ribbon(aes(ymin=0, ymax=ecdf_y, fill=model_family), alpha=0.07, color=NA) +
  geom_step(aes(y=ecdf_y), linewidth=0.9, alpha=0.9) +
  geom_vline(xintercept=c(0.5,0.6,0.8), linetype="dashed",
             color="#FFD700", linewidth=0.5, alpha=0.7) +
  annotate("text", x=c(0.52,0.62,0.82), y=0.08,
           label=c("50%","60%","80%"), color="#FFD700", size=3, hjust=0, fontface="italic") +
  scale_color_manual(values=PALETTE2, name="Model") +
  scale_fill_manual (values=PALETTE2, guide="none") +
  scale_x_continuous(limits=c(0,1.02), breaks=seq(0,1,0.2), labels=percent_format(1)) +
  scale_y_continuous(limits=c(0,1.02), breaks=seq(0,1,0.25), labels=percent_format(1)) +
  labs(title="Cumulative Score Distribution (ECDF)",
       subtitle="Dashed lines = 0.5 / 0.6 / 0.8 score thresholds",
       x="Final Score", y="Cumulative Proportion of Tasks") +
  dark_theme

ggplotly(p_ecdf) %>%
  layout(paper_bgcolor=DARK_BG, plot_bgcolor=DARK_PANEL, font=list(color=TEXT_CLR))
```

## Task Coverage Treemap

```{r treemap, fig.width=12, fig.height=7}
if (requireNamespace("treemapify", quietly=TRUE)) {
  library(treemapify)
  task_tree <- df_complete %>%
    filter(model_family %in% COMPLETE) %>%
    group_by(tier, task_type) %>%
    summarise(avg_score=mean(final_score,na.rm=TRUE),
              n_tasks=n()/length(COMPLETE), .groups="drop") %>%
    mutate(tier_lab=paste0("Tier ", tier))

  p_tm <- ggplot(task_tree,
                 aes(area=n_tasks, fill=avg_score, label=task_type, subgroup=tier_lab)) +
    geom_treemap(color=DARK_BG, size=1.5) +
    geom_treemap_subgroup_border(color="#00FFE066", size=3) +
    geom_treemap_subgroup_text(place="topleft", grow=FALSE, reflow=TRUE,
      color=ACCENT, alpha=0.9, fontface="bold", size=10) +
    geom_treemap_text(color="white", alpha=0.85, size=8, place="centre", reflow=TRUE) +
    scale_fill_gradient2(low="#FF4757", mid="#FFD700", high="#00FFE0",
                         midpoint=0.5, limits=c(0,1), name="Avg Score",
                         labels=percent_format(1)) +
    labs(title="Task Coverage Treemap — Avg Score by Task Type",
         subtitle="Area ∝ number of tasks · Colour = average model score") +
    theme(plot.background=element_rect(fill=DARK_BG, color=NA),
          legend.background=element_rect(fill=DARK_BG, color=NA),
          legend.text=element_text(color=TEXT_CLR),
          legend.title=element_text(color=ACCENT, face="bold"),
          plot.title=element_text(color=ACCENT, face="bold", size=13, hjust=0.5),
          plot.subtitle=element_text(color=TEXT_CLR, size=8.5, hjust=0.5))
  p_tm
} else {
  cat("treemapify not installed — run `install.packages('treemapify')`")
}
```

## Model × Model Correlation

```{r correlation, fig.width=10, fig.height=5}
wide_model <- df_complete %>%
  filter(model_family %in% COMPLETE) %>%
  select(task_id, model_family, final_score) %>%
  tidyr::pivot_wider(names_from=model_family, values_from=final_score)

cor_mat <- cor(wide_model[, COMPLETE], use="pairwise.complete.obs")

cor_long <- as.data.frame(as.table(cor_mat)) %>%
  rename(x=Var1, y=Var2, corr=Freq) %>%
  mutate(x=factor(x, levels=COMPLETE), y=factor(y, levels=rev(COMPLETE)),
         label=sprintf("%.2f", corr))

p_cor <- ggplot(cor_long, aes(x, y, fill=corr)) +
  geom_tile(color=DARK_BG, linewidth=0.8) +
  geom_text(aes(label=label), size=5, color="white", fontface="bold") +
  scale_fill_gradient2(low="#FF4757", mid="#0D1426", high="#00FFE0",
                       midpoint=0, limits=c(-1,1), name="r",
                       guide=guide_colorbar(barheight=6, barwidth=0.8)) +
  coord_fixed() +
  labs(title="Model × Model Score Correlation",
       subtitle="Pairwise Pearson on per-task final scores", x=NULL, y=NULL) +
  dark_theme + theme(panel.grid=element_blank())

ggplotly(p_cor) %>%
  layout(paper_bgcolor=DARK_BG, plot_bgcolor=DARK_PANEL, font=list(color=TEXT_CLR))
```

## Pass Rate Heatmap — Tier × Model

```{r pass-rate-heat, fig.width=8, fig.height=5}
pass_heat <- df_complete %>%
  filter(model_family %in% COMPLETE) %>%
  group_by(tier, model_family) %>%
  summarise(n_pass=sum(final_score>=0.5,na.rm=TRUE), n_total=n(),
            rate=n_pass/n_total, .groups="drop") %>%
  mutate(tier_lab=factor(paste0("Tier ",tier), levels=rev(paste0("Tier ",1:4))),
         model_family=factor(model_family, levels=COMPLETE),
         cell_lbl=sprintf("%d/%d\n(%.0f%%)", n_pass, n_total, rate*100))

p_ph <- ggplot(pass_heat, aes(x=model_family, y=tier_lab, fill=rate)) +
  geom_tile(color=DARK_BG, linewidth=1) +
  geom_text(aes(label=cell_lbl), color="white", size=4, lineheight=1.3, fontface="bold") +
  scale_fill_gradient2(low="#FF4757", mid="#FFD700", high="#00FFE0",
                       midpoint=0.5, limits=c(0,1), name="Pass Rate",
                       labels=percent_format(1)) +
  scale_x_discrete(position="top") +
  labs(title="Pass Rate: Tier × Model",
       subtitle="Cells: tasks passed / total (threshold = 0.50)", x=NULL, y=NULL) +
  dark_theme + theme(panel.grid=element_blank(),
                     axis.text.x=element_text(face="bold", size=11))

ggplotly(p_ph) %>%
  layout(paper_bgcolor=DARK_BG, plot_bgcolor=DARK_PANEL, font=list(color=TEXT_CLR))
```

## Score by Difficulty Level

```{r difficulty-line, fig.width=9, fig.height=6}
DIFF_ORD <- c("basic","intermediate","advanced")
diff_sum2 <- df_complete %>%
  filter(model_family %in% COMPLETE) %>%
  mutate(difficulty=factor(difficulty, levels=DIFF_ORD)) %>%
  group_by(model_family, difficulty) %>%
  summarise(mean_score=mean(final_score,na.rm=TRUE),
            se=sd(final_score,na.rm=TRUE)/sqrt(n()), .groups="drop") %>%
  mutate(diff_num=as.integer(difficulty))

p_diff <- ggplot(diff_sum2, aes(x=diff_num, y=mean_score, color=model_family)) +
  geom_ribbon(aes(ymin=mean_score-se, ymax=mean_score+se, fill=model_family),
              alpha=0.12, color=NA, show.legend=FALSE) +
  geom_hline(yintercept=0.5, linetype="dashed", color="#FFD700",
             linewidth=0.6, alpha=0.7) +
  geom_line(linewidth=1.1, alpha=0.9) +
  geom_point(size=3.5, shape=21, aes(fill=model_family),
             color="white", stroke=0.6, show.legend=FALSE) +
  geom_text(aes(label=sprintf("%.2f",mean_score)), vjust=-1.2, size=3.2, fontface="bold") +
  scale_color_manual(values=PALETTE2, name="Model") +
  scale_fill_manual (values=PALETTE2, guide="none") +
  scale_x_continuous(breaks=1:3, labels=DIFF_ORD, limits=c(0.5,3.5)) +
  scale_y_continuous(limits=c(0,1.08), labels=percent_format(1), breaks=seq(0,1,0.25)) +
  labs(title="Score by Difficulty Level",
       subtitle="Mean ± SE ribbon · Dashed = pass threshold",
       x="Difficulty", y="Average Score") +
  dark_theme

ggplotly(p_diff) %>%
  layout(paper_bgcolor=DARK_BG, plot_bgcolor=DARK_PANEL, font=list(color=TEXT_CLR))
```

## Bar Chart Race — Final Frame

```{r bar-race-frame, fig.width=9, fig.height=5}
tt_ord2 <- df_complete %>%
  filter(model_family %in% COMPLETE) %>%
  group_by(task_type, tier) %>%
  summarise(overall=mean(final_score,na.rm=TRUE), .groups="drop") %>%
  arrange(tier, overall) %>%
  pull(task_type)

final_race <- df_complete %>%
  filter(model_family %in% COMPLETE) %>%
  group_by(model_family) %>%
  summarise(cum_avg=mean(final_score,na.rm=TRUE), .groups="drop") %>%
  mutate(model_family=factor(model_family, levels=COMPLETE))

p_race_final <- ggplot(final_race,
                       aes(x=reorder(model_family,-cum_avg), y=cum_avg, fill=model_family)) +
  geom_col(width=0.72, alpha=0.9, color=NA) +
  geom_text(aes(label=sprintf("%.3f",cum_avg)), hjust=-0.12, size=5,
            color=TEXT_CLR, fontface="bold") +
  geom_hline(yintercept=0.5, linetype="dashed", color="#FFD700",
             linewidth=0.7, alpha=0.8) +
  coord_flip(clip="off") +
  scale_fill_manual(values=PALETTE2, guide="none") +
  scale_y_continuous(limits=c(0,1.12), labels=percent_format(1)) +
  labs(title="Overall Average Score — Final Standings",
       subtitle="Dashed = pass threshold (0.50)",
       x=NULL, y="Average Score") +
  dark_theme +
  theme(panel.grid.major.y=element_blank(),
        plot.margin=margin(16,60,16,16))

p_race_final
```

<div class="info-box">
**Animated version:** `figures/15_bar_race.gif` — cumulative score per model as each task type is revealed in order.
</div>

---

# Appendix — Full Run Data

All `r nrow(df_complete)` task runs (4 complete models). Use the search box to filter.

```{r appendix-table}
dt_data <- df_complete %>%
  select(
    run_id, model_family, task_id, task_type, tier, difficulty,
    final_score, numeric_score, structure_score, assumption_score,
    pass, answer_found, latency_ms, error
  ) %>%
  mutate(
    final_score      = round(final_score, 3),
    numeric_score    = round(numeric_score, 3),
    structure_score  = round(structure_score, 3),
    assumption_score = round(assumption_score, 3),
    latency_ms       = round(latency_ms, 0),
    pass             = as.character(pass),
    answer_found     = as.character(answer_found),
    error            = ifelse(is.na(error), "", error)
  )

DT::datatable(
  dt_data,
  rownames  = FALSE,
  filter    = "top",
  extensions = "Buttons",
  options   = list(
    pageLength  = 25,
    scrollX     = TRUE,
    dom         = "Blfrtip",
    buttons     = c("copy", "csv", "excel"),
    columnDefs  = list(
      list(width = "80px",  targets = c(0)),
      list(width = "70px",  targets = c(4, 5)),
      list(width = "90px",  targets = c(6, 7, 8, 9)),
      list(width = "65px",  targets = c(10, 11))
    ),
    initComplete = DT::JS(
      "function(settings, json) {",
      "  $(this.api().table().header()).css({'background-color':'#0D1535','color':'#00FFE0'});",
      "}"
    )
  ),
  class = "display compact"
) %>%
  DT::formatStyle(
    "pass",
    backgroundColor = DT::styleEqual(c("TRUE","FALSE"), c("#0D4F3C","#3D1020")),
    color           = DT::styleEqual(c("TRUE","FALSE"), c("#7FFFD4","#FF6B6B"))
  ) %>%
  DT::formatStyle(
    "final_score",
    background = DT::styleColorBar(c(0,1), "#00CED133"),
    backgroundSize = "100% 88%",
    backgroundRepeat = "no-repeat",
    backgroundPosition = "center"
  )
```

---

*Report generated on `r Sys.Date()` · DS 299 Capstone · Powered by R + ggplot2 + plotly*

---

# References

Bolstad, W. M. (2007). *Introduction to Bayesian Statistics* (2nd ed.). Wiley.

Bishop, C. M. (2006). *Pattern Recognition and Machine Learning*. Springer.

Hoff, P. D. (2009). *A First Course in Bayesian Statistical Methods*. Springer.

Carlin, B. P., & Louis, T. A. (2008). *Bayesian Methods for Data Analysis* (3rd ed.). Chapman & Hall/CRC.

Ghosh, J. K., Delampady, M., & Samanta, T. (2006). *An Introduction to Bayesian Analysis: Theory and Methods*. Springer.

Lee, P. M. (2012). *Bayesian Statistics: An Introduction* (4th ed.). Wiley.

Goldstein, M., & Wooff, D. (2007). *Bayes Linear Statistics: Theory and Methods*. Wiley.

**Benchmark Methodology References**

Lu, Y., Yang, R., Zhang, Y., et al. (2025). StatEval: A Comprehensive Benchmark for Large Language Models in Statistics. *arXiv:2510.09517*

Nagarkar, C., et al. (2026). Can LLM Reasoning Be Trusted? A Comparative Study: Using Human Benchmarking on Statistical Tasks. *arXiv:2601.14479*

Liu, T., Chen, Z., Fang, Z., et al. (2025). MathEval: A Comprehensive Benchmark for Evaluating Large Language Models on Mathematical Reasoning Capabilities. *Frontiers of Digital Education, 2*, 16. https://doi.org/10.1007/s44366-025-0053-z

Chen, W., Ma, X., Wang, X., & Cohen, W. W. (2022). Program of Thoughts Prompting: Disentangling Computation from Reasoning for Numerical Reasoning Tasks. *arXiv:2211.12588*

Wei, J., Wang, X., Schuurmans, D., et al. (2022). Chain-of-Thought Prompting Elicits Reasoning in Large Language Models. *arXiv:2201.11903*
