% --- Section: Abstract ---

\begin{abstract}
Accuracy-only leaderboards disguise the actual failure modes of LLMs
when used for solving statistical problems. Five frontier
models --- Claude Sonnet 4.5, GPT-4.1, Gemini 2.5 Flash, DeepSeek-Chat,
Mistral Large --- are benchmarked on 171 Bayesian and inferential
statistics tasks across 38 topics. Furthermore, three axes
perturbations --- rephrasing, numerical change, and semantic change ---
are also applied, summing up to a total of 473. Each response is
scored twice, by a Python-based deterministic keyword rubric and by an
out-of-family independent AI judge --- Llama 3.3 70B Turbo via
Together AI on assumption articulation and
reasoning quality. Three leaderboards are derived from the results.
GPT-4.1 is first on robustness to prompt variation (0.9996), but
ranks third on NMACR accuracy (0.673). Claude leads
in verbalized extraction of self-confidence (ECE 0.033) and places
second on NMACR accuracy (0.698), but drops to
fourth in robustness to prompt variation (0.9565). 44.3\% of computed 750 paired (task, response)
outputs fail on the assumption-compliance dimension (no mention of
assumption derivation). Among 143 judge-flagged Level-1
(assumption-compliance) failures, 67 (46.9\%) are assumption
violations. There is a moderate
agreement on assumption compliance between the keyword rubric (regex
from Python-based ground-truth) and the Llama judge, with a Spearman
$\rho = 0.602$ on assumption compliance, essentially zero
($\rho = 0.004$) on method structure, and weak agreement
($\rho = 0.180$) on reasoning quality. A single-metric leaderboard is
the wrong approach in such evaluations, so a deeper and
multi-dimensional assessment will serve as a stronger foundation.
\end{abstract}

\begin{IEEEkeywords}
LLMs, Bayes' theorem, calibration, perturbation robustness,
expected calibration error, LLM-as-judge, benchmark
\end{IEEEkeywords}
