% --- Section: Introduction ---
% Drafted Phase 5 — values pulled from cleanup/04_phase5_data_pulled.md
% Target: ~600–800 words.

\section{Introduction}
\label{sec:intro}

Large language models are now routine collaborators in scientific and
quantitative work, including settings where the user reads a leaderboard
number, picks the top model, and trusts its output. This habit is
becoming consequential. Statistical-reasoning benchmarks such as
StatEval~\cite{lu2025stateval}, MathEval~\cite{liu2025matheval}, and
the human-comparison study of Nagarkar et al.~\cite{nagarkar2026canllm}
report accuracy in a single dimension, and ad-hoc evaluations on
Bayesian and inferential tasks~\cite{longjohn2025bayesian} continue this
pattern. A single accuracy score, however, fuses three properties that
matter independently to a downstream user: how often the model lands on
the right number; how stably it does so when the prompt is reworded or
the numerical setup shifts; and how well its stated confidence tracks
its empirical correctness. When these properties disagree, the
leaderboard is misleading.

This paper makes that disagreement concrete on a benchmark of 171
Bayesian and inferential tasks. We score five frontier LLMs on three
axes--accuracy, robustness, and calibration--and observe non-trivial
reordering across axes. Two patterns drive the headline. First, the
model with the lowest base accuracy in our benchmark (ChatGPT, 0.621)
is the best on robustness (0.9996), with essentially no degradation
between base prompts and perturbed prompts. Second, the model that
leads both accuracy (Claude, 0.683) and binary-pass calibration
(Claude, ECE 0.0334) ranks fourth of five on robustness (0.9565), a
three-percentage-point drop under perturbation. Both patterns are
invisible on a single-metric leaderboard, and each implies different
deployment advice. Beyond the rank shifts, 44.3 percent of responses
fail to explicitly state the statistical assumptions their derivations
require--despite often using those assumptions implicitly--and
assumption violation is the dominant failure mode at 47 percent of
judge-classified failures. This echoes the assumption-blindness pattern
identified outside Bayesian inference by Du et al.~\cite{du2025icecream}
in causal reasoning.

The methodological gap that produced these findings is also worth
naming. Most LLM-statistics evaluations score on a keyword rubric or a
single-judge protocol; both have known biases. Keyword rubrics conflate
surface form with substance: writing the word ``assume'' is not the
same as actually stating an assumption. Single-judge protocols carry
self-preference bias and design-choice sensitivity, as catalogued by
Yamauchi et al.~\cite{park2025judge} and Feuer et al.~\cite{judgment2025noise}.
We address both: each response is independently scored by a
deterministic keyword rubric (the live runner) and an external,
out-of-family judge--Llama 3.3 70B Turbo, served via Together AI, which
is not one of the five benchmarked models. The two scoring paths
disagree where it matters: keyword and judge agreement on
assumption-compliance is moderate (Spearman 0.602), while on method
structure and reasoning quality the two views diverge almost entirely.
The keyword rubric is systematically more lenient on assumptions (71.1
percent pass vs 55.7 percent from the judge), which explains why
keyword-only protocols overestimate model competence on Bayesian
problems specifically.

Our contributions are:
\begin{enumerate}
  \item A benchmark of 171 Bayesian and inferential tasks (136 closed-form
        conjugate models and 35 computational Bayesian methods spanning
        Gibbs, Metropolis-Hastings, HMC, RJMCMC, hierarchical, VB, and
        ABC) augmented with 473 principled perturbations across three
        axes--rephrase, semantic, and numerical--covering all 38 task
        types in the suite.
  \item An external-judge protocol that uses an out-of-family open-weights
        model (Llama 3.3 70B Turbo) to score assumption-compliance and
        reasoning quality, with the keyword-rubric vs judge agreement
        characterised per dimension (Spearman 0.602 on
        assumption-compliance, far lower elsewhere). This separates
        rubric-detectable form from judge-detectable substance.
  \item Empirical evidence that accuracy, robustness, and calibration
        rankings of the same five frontier LLMs disagree non-trivially.
        The two flagship divergences are a 5-to-1 inversion between
        accuracy and robustness (ChatGPT) and a 1, 1, 4 pattern for the
        accuracy-and-calibration leader (Claude), neither of which is
        legible from a single-metric leaderboard.
  \item An open methodology and audit trail: NMACR scoring weights
        (literature-derived, A=0.30, R=0.25, M=0.20, C=0.15, N=0.10),
        aggregation choices, and tolerance thresholds are all
        documented, reproducible, and traceable to the source papers
        that motivated them.
\end{enumerate}

The remainder of the paper is organised as follows.
Section~\ref{sec:related} reviews statistical-reasoning benchmarks, the
calibration literature~\cite{guo2017calibration}, and LLM-as-judge
methodology~\cite{zheng2023judge,park2025judge,judgment2025noise}.
Section~\ref{sec:methodology} describes the task suite, perturbation
taxonomy, and judge protocol. Section~\ref{sec:setup} details the five
benchmarked models, scoring paths, and ECE computation.
Section~\ref{sec:results} presents the three rankings and supporting
analyses. Section~\ref{sec:discussion} argues that the divergence is
principled, not noise. Section~\ref{sec:threats} catalogs threats to
validity, and Section~\ref{sec:conclusion} closes.
