% --- Section: Related Work ---
% Drafted Phase 6 — values pulled from cleanup/04_phase5_data_pulled.md
% Target: ~400 words.

\section{Literature Review}
\label{sec:related}

\textbf{LLM benchmarks for quantitative reasoning.} Statistical and
mathematical reasoning benchmarks have proliferated in the past two
years. StatEval~\cite{lu2025stateval} catalogues 13{,}817 problems
across descriptive statistics, probability, inference, and regression,
scored primarily by answer correctness. MathEval~\cite{liu2025matheval}
aggregates 19 datasets to compare 23 LLMs on mathematical reasoning,
again with accuracy as the headline metric. Nagarkar et
al.~\cite{nagarkar2026canllm} compare LLMs against human respondents
on statistical tasks. All three measure how often the model lands on
the right number; none separately measure whether the reasoning that
produced the number is well-formed or robust to perturbation.

\textbf{Bayesian-reasoning evaluation.} Longjohn et
al.~\cite{longjohn2025bayesian} propose a Bayesian framework for
evaluating LLM behavior probabilistically, but the focus is on
posterior-based aggregation of benchmark results, not on Bayesian
reasoning as a task. Du et al.~\cite{du2025icecream} document
assumption-blindness in causal reasoning, finding that LLMs often
produce ``convincing yet misleading'' answers without articulating
the assumptions those answers depend on. Our finding that 44.3 percent
of Bayesian responses fail to state required assumptions extends this
pattern to inferential statistics specifically.

\textbf{Calibration.} Guo et al.~\cite{guo2017calibration} introduced
Expected Calibration Error (ECE) and showed that modern neural
networks are systematically miscalibrated despite high accuracy. ECE
is well-studied for classifiers; its application to free-form LLM
reasoning is recent and methodologically less settled. FermiEval and
related work~\cite{fermieval2025,multianswer2026,nagarkar2026canllm}
adapt calibration to natural-language outputs but typically along a
single dimension. We compute binary-pass ECE plus per-NMACR-dimension
ECE.

\textbf{LLM-as-judge.} Zheng et al.~\cite{zheng2023judge} popularised
LLM-as-judge with MT-Bench, demonstrating that strong LLMs can
substitute for human raters on open-ended tasks. Subsequent work
catalogs design-choice sensitivity and self-preference
bias~\cite{park2025judge,judgment2025noise}. Brittlebench and
ReasonBench~\cite{brittlebench2026,reasonbench2025} document prompt
sensitivity and reasoning instability under perturbation. Our protocol
constrains the judge to a single dimension (assumption-compliance) and
uses an out-of-family open-weights model (Llama 3.3 70B Turbo), which
together address two of the failure modes catalogued by Feuer et
al.~\cite{judgment2025noise}.

Across these threads, evaluation typically collapses to a single
accuracy or pass-rate number. We synthesize the three threads
--- accuracy, robustness, and calibration --- into a tri-axis
ranking framework and show that the resulting rank orders disagree
non-trivially for the same five frontier LLMs on the same task suite.

\textbf{Positioning.} Prior work treats accuracy, robustness, and
calibration as separable evaluation concerns and addresses them in
isolation. Benchmarks for quantitative reasoning measure accuracy at
scale but rarely report robustness or
calibration~\cite{lu2025stateval,liu2025matheval,nagarkar2026canllm}.
Calibration studies operate on classification or short-answer
formats, not on the free-form numerical and prose responses typical
of Bayesian reasoning~\cite{guo2017calibration}. LLM-as-judge work has
matured into a default validation tool but is most often applied as a
holistic preference signal that carries documented
biases~\cite{zheng2023judge,park2025judge,judgment2025noise}. To our
knowledge, no prior benchmark for Bayesian or inferential statistical
reasoning combines (i) a principled perturbation taxonomy for
robustness, (ii) an external single-dimension judge protocol for
assumption-compliance, and (iii) calibration measured directly on the
same task set. Our contribution is the multi-axis framework that
surfaces ranking divergences hidden by single-metric leaderboards.
