% --- Section: Conclusion ---

\section{Discussion and Conclusion}
\label{sec:conclusion}

Five frontier LLMs were benchmarked on 171 Bayesian and inferential
tasks with 473 perturbations, scored by a keyword rubric, an NMACR
aggregator with literature-derived weights, and an out-of-family
Llama 3.3 70B Turbo judge constrained to assumption-compliance. The
five models produce three different rank orders: GPT-4.1, third on
accuracy ($0.673$), is most robust ($0.9996$). Claude, second on
accuracy ($0.698$) and top on calibration (ECE $0.033$), drops to
fourth on robustness ($0.9565$).
$44.3\%$ of responses do not articulate the required assumptions,
and the keyword rubric overcounts assumption articulation by
$15.4$ points relative to the judge. A single number is the wrong
instrument for statistical-reasoning evaluation.

\textbf{Threats to validity.} The judge can carry training biases;
it is constrained to one dimension and validated against the keyword
rubric (Spearman $\rho = 0.602$). The same Llama 3.3 70B Turbo
model both generated the v2 perturbations and served as the judge;
it evaluates outputs from the five benchmarked LLMs (not Llama
outputs), so this is not strict self-judging, but Llama-flavored
perturbation phrasing could yield more consistent judge scoring
than human-flavored phrasing. Krippendorff's $\alpha$ sits in the
``questionable'' range, reflecting genuine ambiguity in scoring
free-form Bayesian reasoning. The three-ranking divergence is a
within-model finding independent of inter-rater agreement. Task
coverage excludes causal inference and experimental design. Model
versions are May 2026 snapshots; inversion patterns may not
replicate as APIs evolve.

\textbf{Future work.} The four-axis decomposition in
\S\ref{sec:extended-diagnostics} opens several extensions of this
evaluation framework. The task suite can broaden to causal
inference, experimental design, and frequentist hypothesis testing,
where assumption articulation matters as much as in Bayesian
inference. The single-dimension judge can extend to a multi-judge
ensemble with Krippendorff $\alpha$ reported across raters rather
than against the keyword rubric only, bounding judge-bias variance
more rigorously than the single-rater estimate in
\S\ref{sec:assumption-compliance}. The per-model over-credit
asymmetry surfaced in \S\ref{sec:per-model-disagreement}
(Mistral $12.11\times$, Claude $7.84\times$) invites mechanistic
investigation: an RLHF artifact, a training-data composition
effect, or an attention-pattern signature on
assumption-articulation tokens. The Phase~2 zero-failure result
in \S\ref{sec:failure-by-task-type} motivates a rubric redesign
that scores procedural assumption articulation --- convergence
diagnostics, proposal-distribution choice, acceptance-rate
calibration --- rather than only conjugate-derivation assumptions.
The rephrasing-sensitivity result in
\S\ref{sec:per-axis-robustness} (rephrasing damages scores more
than numerical perturbation) suggests adversarial perturbation
generation targeting the most failure-prone task types from
\S\ref{sec:failure-by-task-type} as a probe corpus for future
model releases. Finally, the GPT-4.1 robustness inversion
deserves controlled provider-level experiments isolating
training-data and decoding choices.
