% --- Appendix A: Formal Metric Definitions ---
% Drafted Phase 7. Restates Eqs 1-3 from §III in detail and adds Eqs 4-5
% (Krippendorff α, Spearman ρ) plus a bootstrap-procedure paragraph.

\label{app:metrics}

This appendix collects formal definitions for the five quantitative
metrics referenced in the main text and the bootstrap procedure used
for all reported confidence intervals.

\subsection{NMACR Aggregate}

For each (task, model) pair, the Path~B rubric produces five
dimension-level scores $N, M, A, C, R \in [0,1]$. The aggregate
score from~(\ref{eq:nmacr}), restated here,
\[
  S_{\text{NMACR}} = 0.10\,N + 0.20\,M + 0.30\,A + 0.15\,C + 0.25\,R.
\]
The ordering $A > R > M > C > N$ comes from weighting assumption
articulation highest in a Bayesian-reasoning task and weighting a
correct number with no derivation lowest. Per-model accuracy is
the mean of $S_{\text{NMACR}}$ over the 171 base tasks. The
literature trail behind the weights lives in the scoring metadata.

\subsection{Robustness Pass-Flip}

Equation~(\ref{eq:robustness}) defines per-model robustness as one
minus the mean absolute pass-flip between a base task and the mean
pass over its perturbations. Equivalently, for each base task with
$k$ perturbations, the contribution to $R_m$ is
\[
  \frac{1}{k}\sum_{p \in \mathcal{P}(t)}
    \mathbb{1}\bigl[\mathrm{pass}(t, m) = \mathrm{pass}(p, m)\bigr].
\]
The two formulations agree exactly for binary $\mathrm{pass}(\cdot)$.

\subsection{Expected Calibration Error}

Binary-pass ECE is computed with $B = 4$ confidence buckets parsed
from the response's hedging language (low, medium, high, unstated).
Following the formulation of Guo et al.~\cite{guo2017calibration} and
restating~(\ref{eq:ece}),
\[
  \mathrm{ECE} = \sum_{b=1}^{4} \frac{|B_b|}{N}
                 \,\bigl|\,\mathrm{acc}(B_b) - \mathrm{conf}(B_b)\,\bigr|,
\]
where the bucket centres for ``low'', ``medium'', ``high'', and
``unstated'' are mapped to $0.25$, $0.50$, $0.85$, and $0.50$
respectively before computing $\mathrm{conf}(B_b)$.

\subsection{Krippendorff's $\alpha$}

For each judged dimension, inter-rater reliability between the
keyword rubric and the external judge is measured by
\begin{equation}
  \alpha = 1 - \frac{D_o}{D_e},
  \label{eq:krippendorff}
\end{equation}
where $D_o$ is the observed disagreement among raters and $D_e$ is
the disagreement expected under chance. Values near $1$ indicate
strong agreement; values near $0$ indicate chance-level agreement.
We compute $\alpha$ on the three Path~B dimensions
(method-structure, assumption-compliance, reasoning-quality) used
to characterize keyword-vs-judge alignment in Section~\ref{sec:results}.

\subsection{Spearman Rank Correlation}

Per-dimension keyword-vs-judge agreement is also reported as a
Spearman rank correlation,
\begin{equation}
  \rho = 1 - \frac{6 \sum_{i=1}^{n} d_i^2}{n(n^2 - 1)},
  \label{eq:spearman}
\end{equation}
where $d_i$ is the rank difference between the keyword-rubric
score and the external-judge score for the $i$-th response in the
paired sample of size $n$. We report Spearman $\rho$ rather than
Pearson $r$ because the rubric--judge relationship is monotonic
but not linear.

\subsection{Bootstrap Procedure}

All reported confidence intervals use the 95\% percentile bootstrap
method on per-run aggregates, with $B = 10{,}000$ resamples and a
fixed RNG seed (42) for reproducibility. The resampling unit is the
individual (task, model) run; resamples preserve the per-model count
($n = 171$ for accuracy, $n = 398$ for the v2 perturbation pool used
in robustness). Confidence intervals are reported throughout the
results section as $[\text{lower}, \text{upper}]$ at the $0.025$ and
$0.975$ quantiles of the resampled statistic distribution.
